%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\chapter{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications scientifiques}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Articles primaires}

\subsubsection{Dans des revues à comité de lecture}

\begin{enumerate}
\item %[Delmar {\em et al.} (2005)]{DRL05}%
{\sc Delmar, P.}, {\sc Robin, S.}, {\sc Le~Roux, D.} et {\sc Daudin, J.-J.}
\newblock (2005).
\newblock Mixture model on the variance for the differential analysis of gene
  expression.
\newblock {\em J. R. Statist. Soc. C}.
\newblock {\bf 54}~{\bf (1)} 31--50.

\item %[Ledent et Robin (2005)]{LeR05}%
{\sc Ledent, S.} et {\sc Robin, S.}
\newblock (2005).
\newblock Checking homogeneity of patterns distribution in heterogeneous
  sequences.
\newblock {\em J. Comp. Biol.}
\newblock {\it à paraître}.

\item %[Lorino {\em et al.} (2005)]{LSR05}%
{\sc Lorino, T.}, {\sc Sanaa, M.}, {\sc Robin, S.} et {\sc Daudin, J.-J.}
\newblock (2005).
\newblock Comparison of semiparametric regression models for correlated
  survival data.
\newblock {\em Comm. Statist. Simulations}.
\newblock {\bf 33}~{\bf (8)} 1944--1975.

\item %[Mortier {\em et al.}]{MRL05}%
{\sc Mortier, F.}, {\sc Robin, S.}, {\sc Lassalvy, S.}, {\sc Baril, C.} et {\sc
  Bar-Hen, A.}
\newblock Prediction of euclidean distances with discrete and continuous
  outcomes.
\newblock {\it Under review in J. Mult. Anal.}

\item %[Picard {\em et al.} (2005)]{PRL05}%
{\sc Picard, F.}, {\sc Robin, S.}, {\sc Lavielle, M.}, {\sc Vaisse, C.} et {\sc
  Daudin, J.-J.}
\newblock (2005).
\newblock A statistical approach for array cgh data analysis.
\newblock {\bf 6}~{\bf (27)}. \\
\newblock {\tt www.biomedcentral.com/1471-2105/6/27}.

\item %[Stefanov {\em et al.}]{SRS05}%
{\sc Stefanov, V.}, {\sc Robin, S.} et {\sc Schbath, S.}
\newblock Waiting times for clumps of patterns and for structured motifs in
  random sequences.
\newblock {\it En seconde lecture à Discrete Appl. Math.}

\item %[Aubert {\em et al.} (2004)]{ABD04}%
{\sc Aubert, J.}, {\sc Bar-Hen, A.}, {\sc Daudin, J.-J.} et {\sc Robin, S.}
\newblock (2004).
\newblock Determination of the regulated genes in microarrayexperiments using
  local {FDR}.
\newblock {\bf 5}~{\bf (1)}. \\
\newblock {\tt www.biomedcentral.com/1471-2105/5/125/}.

\item %[Delmar {\em et al.} (2004)]{DRD04}%
{\sc Delmar, P.}, {\sc Robin, S.} et {\sc Daudin, J.-J.}
\newblock (2004).
\newblock Varmixt : Efficient variance modelling for the differential analysis
  of replicated gene expression data.
\newblock {\em Bioinformatics}.
\newblock {\it à paraître}.

\item %[Mary-Huard {\em et al.} (2004)]{MRD04}%
{\sc Mary-Huard, T.}, {\sc Robin, S.}, {\sc Daudin, J.}, {\sc Bitton, F.}, {\sc
  Cabannes, E.} et {\sc Hilson, P.}
\newblock (2004).
\newblock Spotting effect in microarray experiments.
\newblock {\em BMC Bioinformatics}.
\newblock {\bf 5}~{\bf (63)} 1--9. \\
\newblock {\tt www.biomedcentral.com/1471-2105/5/63}.

\item %[Bar-Hen et Robin (2003)]{BaR03}%
{\sc Bar-Hen, A.} et {\sc Robin, S.}
\newblock (2003).
\newblock An iterative procedure for differential analysis of gene expression.
\newblock {\em C.-R. Acad. Sciences}.
\newblock  343--346.

\item %[Mouille {\em et al.} (2003)]{MRL03}%
{\sc Mouille, G.}, {\sc Robin, S.}, {\sc Lecomte, M.}, {\sc Pagant, S.} et {\sc
  H., H.}
\newblock (2003).
\newblock Classification and identification of arabidopsis cell wall mutants
  using fourier transfrom infrared ({FT-IR}) microspectroscopy.
\newblock {\em The Plant J.}
\newblock  393--404.

\item %[Robin {\em et al.} (2003b)]{RLH03}%
{\sc Robin, S.}, {\sc Lecomte, M.}, {\sc Höfte, H.} et {\sc Mouille, G.}
\newblock (2003).
\newblock A procedure for the clustering of cell wall mutants in the model
  plant {\sl arabidopsis} based on fourier-transform infrared ({FT-IR})
  spectroscopy.
\newblock {\em J. Appl. Statist.}.
\newblock {\bf 30}~{\bf (6)} 669--681.

\item %[Bacro {\em et al.} (2002)]{BDM02}%
{\sc Bacro, J.-N.}, {\sc Daudin, J.-J.}, {\sc Mercier, S.} et {\sc Robin, S.}
\newblock (2002).
\newblock Back to the local score in the logarithmic case: a direct and simple
  proof.
\newblock {\em Ann. Inst. Statist. Math.}
\newblock {\bf 54} 748--757.

\item %[Robin {\em et al.} (2002)]{RDR02}%
{\sc Robin, S.}, {\sc Daudin, J.-J.}, {\sc Richard, H.}, {\sc Sagot, M.-F.} et
  {\sc Schbath, S.}
\newblock (2002).
\newblock Occurrence probability of structured motifs in random sequences.
\newblock {\em J. Comp. Biol.}
\newblock {\bf 9} 761--773.

\item %[Nuel {\em et al.} (2001a)]{NRB01}%
{\sc Nuel, G.}, {\sc Robin, S.} et {\sc Baril, C.}
\newblock (2001).
\newblock Predicting phenotypic distances using a linear model: the case of
  varietal distinctness.
\newblock {\em J. Appl. Statist.}
\newblock {\bf 28}~{\bf (5)} 607--621.

\item %[Nuel {\em et al.} (2001b)]{NBR01}%
{\sc Nuel, G.}, {\sc Baril, C.} et {\sc Robin, S.}
\newblock (2001).
\newblock Varietal distinctness assisted by molecular markers: A methodological
  approach.
\newblock {\em Acta Horticulturae}.
\newblock {\bf 546} 65--71.

\item %[Robin et Daudin (2001)]{RoD01}%
{\sc Robin, S.} et {\sc Daudin, J.-J.}
\newblock (2001).
\newblock Exact distribution of the distances between any occurrences of a set
  of words.
\newblock {\em Ann. Inst. Statist. Math.}
\newblock {\bf 36}~{\bf (4)} 895--905.

\item %[Robin et Schbath (2001)]{RoS01}%
{\sc Robin, S.} et {\sc Schbath, S.}
\newblock (2001).
\newblock Numerical comparison of several approximations of the word count
  distribution in random sequences.
\newblock {\em J. Comp. Biol.}
\newblock {\bf 8}~{\bf (4)} 349--359.

\item %[Sekowska {\em et al.} (2001)]{SRD01}%
{\sc Sekowska, A.}, {\sc Robin, S.}, {\sc Daudin, J.-J.}, {\sc Hénaut, A.} et
  {\sc Danchin, A.}
\newblock (2001).
\newblock Extracting biological information from dna arrays: an unexpected link
  between arginine and methionine metabolism in {\sl {b}acillus subtilis}.
\newblock {\em Genome Biology}. 
\newblock {\bf 2}~{\bf (6)} \\
{\tt genomebiology.com/2001/2/6/research/0019.1}.

\item %[Demotes-Mainard {\em et al.} (1999)]{DJR99}%
{\sc Demotes-Mainard, S.}, {\sc Jeuffroy, M.-H.} et {\sc Robin, S.}
\newblock (1999).
\newblock Spike dry matter and nitrogen accumulation before anthesis in wheat
  as affected by nitrogen fertilizer: relationship to kernels per spike.
\newblock {\em Field Crop Research}.
\newblock {\bf 64} 249--259.

\item %[Robin (1999c)]{Rob99}%
{\sc Robin, S.}
\newblock (1999).
\newblock A model for thermograms.
\newblock {\em Biometrics}.
\newblock {\bf 55}~{\bf (1)} 37--43.

\item %[Robin et Daudin (1999)]{RoD99}%
{\sc Robin, S.} et {\sc Daudin, J.-J.}
\newblock (1999).
\newblock Exact distribution of word occurrences in a random sequence of
  letters.
\newblock {\em J. Appl. Prob.}
\newblock {\bf 36} 179--193.

\item %[Sahli {\em et al.} (1997)]{STR97}%
{\sc Sahli, A.}, {\sc Trécourt, P.} et {\sc Robin, S.}
\newblock (1997).
\newblock One sided acceptance sampling by variables: the case of the {L}aplace
  distribution.
\newblock {\em Commun. Statist. - Theory Meth.}
\newblock {\bf 26}~{\bf (11)} 2817--2834.

\item %[Robin (1996b)]{Rob96}%
{\sc Robin, S.}
\newblock (1996).
\newblock Sensitivity analysis of non-parametric tests for censored data.
\newblock {\em Commun. Statist. - Theory Meth.}
\newblock {\bf 25}~{\bf (8)} 1693--1715.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Conférences invitées} \label{Subsubsec:ConfInvit}

\begin{itemize}
\item {\em Predicting phenotypic distances through mocular data}~:
  Electrophoresis (Rouen, 1999).
\item {\em Analyse statistique des données issues de biopuces},
  Journées de la Société Française de Statistique (Bruxelles, 2002)
\item {\em Some Statistical Problems in Microarray Data Analysis}~:
  26th Annual Conference of the Gesellschaft für Klassifikation
(Mannheim, Allemagne, 2002).
\item {\em Répartition de motifs dans des séquences d'ADN}, Journées
  de la Société Française de Statistique (Lyon, 2003)
\item {\em Analyzing Motifs Distribution in DNA Sequences}~:Theme
  Conference of the Royal Statistical Society on Statistical Genetics
  and Bioinformatics (Diepenbeck, Belgique, 2003).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synthèses scientifiques}

\subsubsection{Dans périodique sans comité de lecture}
\begin{enumerate}
\item %[Robin (2003b)]{Rob03b}%
{\sc Robin, S.}
\newblock (2003).
\newblock La juste mesure des g\`{e}nes.
\newblock {\em La Recherche}.
\newblock {\bf (363)} 90--91.
\end{enumerate}


\subsubsection{Chapitres d'ouvrage}
\begin{enumerate}
\item %[Mary-Huard {\em et al.}]{MPR05}%
{\sc Mary-Huard, T.}, {\sc Picard, F.} et {\sc Robin, S.}
\newblock Introduction to statistical methods for microarray data analysis.
\newblock {\it à paraître}.

\item %[Doumas {\em et al.} (2004)]{MoB04}%
{\sc Doumas, P.}, {\sc Rothan, C.} et {\sc Robin, S.}
\newblock (2004).
\newblock {\em La génomique en biologie végétale}.
\newblock (J.-F. Morot-Gaudry et J.-F. Briat,~ed.), chapitre Analyse du
  transcriptome végétal pas les puces à ADN, 155--182.
\newblock Science update. INRA.

\item %[Martin-Magnette et Robin (2004)]{MMR04}%
{\sc Martin-Magnette, M.-L.} et {\sc Robin, S.}
\newblock (2004).
\newblock {\em Informatique pour l'analyse du transcriptome}.
\newblock chapitre Techniques statistique pour l'analyse du transcriptome.
\newblock Hermès.

\item %[Robin (2003a)]{Rob03a}%
{\sc Robin, S.}
\newblock (2003).
\newblock {\em Between Data Science And Applied Data Analysis}.
\newblock (S.~Martin, W.~Gaul, et M.~Vichi,~ed.), chapitre Some Statistical
  Issues in Microarray Data Analysis, 337--347.
\newblock Springer.


\end{enumerate}

\subsubsection{Ouvrages}
\begin{enumerate}
\item %[Robin {\em et al.} (2005)]{RRS05}%
{\sc Robin, S.}, {\sc Rodolphe, F.} et {\sc Schbath, S.}
\newblock (2005).
\newblock {\em {DNA}, words and models}.
\newblock Cambridge University Press, {\it à paraître}.
\item %[Robin {\em et al.} (2003a)]{RRS03}%
{\sc Robin, S.}, {\sc Rodolphe, F.} et {\sc Schbath, S.}
\newblock (2003).
\newblock {\em {ADN}, mots et modèles}.
\newblock Echelles. Belin.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Documents à vocation de transfert}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Travaux personnels}

\subsubsection{Ouvrage}
\begin{enumerate}
\item %[Daudin {\em et al.} (1999)]{DRV99}%
{\sc Daudin, J.-J.}, {\sc Robin, S.} et {\sc Vuillet, C.}
\newblock (1999).
\newblock {\em Statistique inférentielle~: Idées, démarches, exemples}.
\newblock Société Française de Statistique. Presses Universitaires de Rennes.
\end{enumerate}

\subsubsection{Polycopiés et support de cours}
\begin{enumerate}
\item %[Lebarbier et Robin (2004)]{LR-ExModLin}%
{\sc Lebarbier, E.} et {\sc Robin, S.}
\newblock (2004).
\newblock Exemples d'application du modèle linéaire.
\newblock 129p.

\item %[Robin (2003c)]{R-Biopuces}%
{\sc Robin, S.}
\newblock (2003).
\newblock Statistical analysis of microarray data.
\newblock 63p.

\item %[Duby et Robin (2001)]{DR-ACP}%
{\sc Duby, C.} et {\sc Robin, S.}
\newblock (2001).
\newblock Analyse en composantes principales.
\newblock 70p.

\item %[Doursat et Robin (1999)]{DR-SimRV}%
{\sc Doursat, C.} et {\sc Robin, S.}
\newblock (1999).
\newblock Simulating radom values.
\newblock INA PG.

\item %[Pommiès et Robin (1999)]{PR-CM}%
{\sc Pommiès, E.} et {\sc Robin, S.}
\newblock (1999).
\newblock Introduction aux chaînes de markov homogènes.
\newblock 65p.

\item %[Robin (1999a)]{R-CSAGAD}%
{\sc Robin, S.}
\newblock (1999).
\newblock Cours de statistique du {CSAGAD}.
\newblock 200p.

\item %[Robin (1999b)]{R-Attente}%
{\sc Robin, S.}
\newblock (1999).
\newblock Introduction aux files d'attente.
\newblock 35p.

\item %[Robin (1999d)]{R-Poisson}%
{\sc Robin, S.}
\newblock (1999).
\newblock Processus de poisson, introduction aux processus de naissances et
  morts.
\newblock 22p.

\item %[Robin (1998)]{R-ModLin}%
{\sc Robin, S.}
\newblock (1998).
\newblock Rappels et compléments sur le modèle linéaire.
\newblock 17p.

\item %[Daudin {\em et al.} (1996)]{DDRT-Chrono}%
{\sc Daudin, J.-J.}, {\sc Duby, C.}, {\sc Robin, S.} et {\sc Trécourt, P.}
\newblock (1996).
\newblock Analyse des séries chronologiques.
\newblock 70p.

\item %[Robin (1996a)]{R-CompPop}%
{\sc Robin, S.}
\newblock (1996).
\newblock Comparaison de populations.
\newblock 68p.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Travaux encadrés}

\subsubsection{Mémoires de stage de DEA \& DESS}
\begin{description}
\item[{\sl Analyse de thermogrammes~:}] G. Bourguignon (1992), E. Gautherat
  (1995), D. Belhaj (1995)
\item[{\sl Distinction variétale~:}] G. Nuel (1998), N. Legall (1999)
\item[{\sl Occurrences de motifs~:}] C. Jubin (1999), H. Richard (2000) et S.
  Ledent (2001)
\item[{\sl Classification et FT-IR~:}] M. Lecomte (2001)
\item[{\sl Analyse de biopuces~:}] Ph. Hupé, F. Picard et T. Mary-Huard
  (2002), E. Haon-Lasporte (2004)
\end{description}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Dossier-DR2"
%%% End: 
