\begin{itemize}

\item MÈmoire de Habilitation ‡ Diriger des Recherches

\item %[Robin {\em et al.} (2005)]{RRS05}%
  {\sc Robin, S.}, {\sc Rodolphe, F.} et {\sc Schbath, S.}  \newblock
  (2005).  \newblock {\em {DNA}, words and models}.

\item%{RSV07}
  S.~Schbath S.~Robin and V.~Vandewalle.  \newblock Statistical tests
  to compare motif count exceptionalities.  \newblock {\em BMC
    Bioinformatics}, 8(84):1--12, 2007.  \newblock {\tt
    doi:10.1186/1471-2105-8-84}.

\item %{PRL07}
  F.~Picard, S.~Robin, E.~Lebarbier, and J.-J. Daudin.  \newblock A
  segmentation/clustering model for the analysis of array {CGH} data.
  \newblock {\em Biometrics}, pages doi:
  10.1111/j.1541--0420.2006.00729.x, 2007.  \newblock {\it to appear}.

\item %{SRS07}
  V.~Stefanov, S.~Robin, and S.~Schbath.  \newblock Waiting times for
  clumps of patterns and for structured motifs in random sequences.
  \newblock {\em Discrete Appl. Math.}, (155):868--80, 2007.

\item %{RBD07}
  S.~Robin, A.~Bar-Hen, J.-J. Daudin, and L.~Pierre.  \newblock A
  semi-parametric approach for mixture models: Application to local
  false discovery rate estimation.  \newblock {\em Comput. Statist.
    Data Analysis}, 2007.  \newblock {\it to appear}.

\item %{MSB06}
  C.~Matias, S.~Schbath, E.~Birmel\'e, J.-J. Daudin, and S.~Robin.
  \newblock Networks motifs : mean and variance for the count.
  \newblock {\em RevStat}, pages 31--51, 2006. \\
  \newblock {\tt www.ine.pt/revstat/pdf/rs060102.pdf}.

\item %{DRL05}
  P.~Delmar, S.~Robin, D.~Le~Roux, and J.-J. Daudin.  \newblock
  Mixture model on the variance for the differential analysis of gene
  expression.  \newblock {\em J. R. Statist. Soc. C}, 54(1):31--50,
  2005.

\item %{MRD04}
  T.~Mary-Huard, S.~Robin, J.J. Daudin, F.~Bitton, E.~Cabannes, and
  P.~Hilson.  \newblock Spotting effect in microarray experiments.
  \newblock {\em BMC Bioinformatics}, 5(63):1--9, 2004.  \newblock
  {\tt www.biomedcentral.com/1471-2105/5/63}.

\item %{MRL03}
  G.~Mouille, S.~Robin, M.~Lecomte, S.~Pagant, and Hˆfte H.  \newblock
  Classification and identification of arabidopsis cell wall mutants
  using fourier transfrom infrared ({FT-IR}) microspectroscopy.
  \newblock {\em The Plant J.}, pages 393--404, 2003.

\end{itemize}

