%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications scientifiques}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Articles primaires}

\paragraphSR{Dans des revues internationales ŗ comitť de lecture
  (depuis 2001).}

{\sl Plusieurs de ces publications figurent {\it in extenso} dans mon
  mťmoire de HDR.}
\begin{enumerate}
\item%{RSV07}
  S.~Schbath S.~Robin and V.~Vandewalle.  \newblock Statistical tests
  to compare motif count exceptionalities.  \newblock {\em BMC
    Bioinformatics}, 8(84):1--12, 2007.  \\ \newblock {\tt
    doi:10.1186/1471-2105-8-84}.

\item %{PRL07}
  F.~Picard, S.~Robin, E.~Lebarbier, and J.-J. Daudin.  \newblock A
  segmentation/clustering model for the analysis of array {CGH} data.
  \newblock {\em Biometrics}, pages doi:
  10.1111/j.1541--0420.2006.00729.x, 2007.  \newblock {\it to appear}.

\item %{SRS07}
  V.~Stefanov, S.~Robin, and S.~Schbath.  \newblock Waiting times for
  clumps of patterns and for structured motifs in random sequences.
  \newblock {\em Discrete Appl. Math.}, (155):868--80, 2007.

\item %{RBD07}
  S.~Robin, A.~Bar-Hen, J.-J. Daudin, and L.~Pierre.  \newblock A
  semi-parametric approach for mixture models: Application to local
  false discovery rate estimation.  \newblock {\em Comput. Statist.
    Data Analysis}, 2007.  \newblock {\it to appear}.

\item %{MRD07}
  T.~Mary-Huard, S.~Robin, and J.J. Daudin.  \newblock A penalized
  criterion for variable selection in classification.  \newblock {\it
    to appear in J. Mult. Anal.}, 2007.

\item %{MRL06}
  F.~Mortier, S.~Robin, S.~Lassalvy, C.P Baril, and A.~Bar-Hen.
  \newblock Prediction of euclidean distances with discrete and
  continuous outcomes.  \newblock {\em J. Mult. Anal.},
  97(8):1799--1814, 2006.  \\ \newblock {\tt
    dx.doi.org/10.1016/j.jmva.2005.06.010}.

\item %{MSB06}
  C.~Matias, S.~Schbath, E.~Birmel\'e, J.-J. Daudin, and S.~Robin.
  \newblock Networks motifs : mean and variance for the count.
  \newblock {\em RevStat}, pages 31--51, 2006. \\
  \newblock {\tt www.ine.pt/revstat/pdf/rs060102.pdf}.

\item %{LeR05}
  S.~Ledent and S.~Robin.  \newblock Checking homogeneity of patterns
  distribution in heterogeneous sequences.
  \newblock {\em J. Comp. Biol.}, 12(6):672--85, Jul 2005. \\
  \newblock {\tt
    www.liebertonline.com/doi/abs/10.1089/cmb.2005.12.672}.

\item %{DRL05}
  P.~Delmar, S.~Robin, D.~Le~Roux, and J.-J. Daudin.  \newblock
  Mixture model on the variance for the differential analysis of gene
  expression.  \newblock {\em J. R. Statist. Soc. C}, 54(1):31--50,
  2005.

\item %{LDR05}
  T.~Lorino, J.-J. Daudin, S.~Robin, and M.~Sanaa.  \newblock Factors
  associated with time to neonatal diarrhoea in french beef calves.
  \newblock {\em Prevent. Veterin. Med.}, 68(2--4):91--102, 2005.

\item %{PRL05}
  F.~Picard, S.~Robin, M.~Lavielle, C.~Vaisse, and J.-J. Daudin.
  \newblock A statistical approach for array {CGH} data analysis.
  \newblock {\em BMC Bioinformatics}, 6(27):1, 2005. 
  \\ \newblock {\tt www.biomedcentral.com/1471-2105/6/27}.

\item %{ABD04}
  J.~Aubert, A.~Bar-Hen, J.-J. Daudin, and S.~Robin.  \newblock
  Determination of the regulated genes in microarray experiments using
  local {FDR}.  \newblock {\em BMC Bioinformatics}, 5(125):1--9, 2004.
  \\ \newblock {\tt www.biomedcentral.com/1471-2105/5/125/}.

\item %{MRD04}
  T.~Mary-Huard, S.~Robin, J.J. Daudin, F.~Bitton, E.~Cabannes, and
  P.~Hilson.  \newblock Spotting effect in microarray experiments.
  \newblock {\em BMC Bioinformatics}, 5(63):1--9, 2004.  \\ \newblock
  {\tt www.biomedcentral.com/1471-2105/5/63}.

\item %{DRD05}
  P.~Delmar, S.~Robin, and J.-J. Daudin.  \newblock Varmixt :
  Efficient variance modelling for the differential analysis of
  replicated gene expression data.  \newblock {\em Bioinformatics},
  21(4):502--8, 2005.  \\ \newblock {\tt
    doi:10.1093/bioinformatics/bti023}.

\item %{LSR04}
  T.~Lorino, M.~Sanaa, S.~Robin, and J.-J Daudin.  \newblock
  Comparison of semiparametric regression models for correlated
  survival data.  \newblock {\em Comm. Statist. Simulations},
  33(8):1944--1975, 2004.

\item %{MRL03}
  G.~Mouille, S.~Robin, M.~Lecomte, S.~Pagant, and HŲfte H.  \newblock
  Classification and identification of arabidopsis cell wall mutants
  using fourier transfrom infrared ({FT-IR}) microspectroscopy.
  \newblock {\em The Plant J.}, pages 393--404, 2003.

\item %{RLH03}
  S.~Robin, M.~Lecomte, H.~HŲfte, and G.~Mouille.  \newblock A
  procedure for the clustering of cell wall mutants in the model plant
  {\sl arabidopsis} based on fourier-transform infrared ({FT-IR})
  spectroscopy.  \newblock {\em J. Appl. Statist.}, 30(6):669--681,
  2003.

\item %{Rob03a}
  S.~Robin.  \newblock {\em Between Data Science And Applied Data
    Analysis}, chapitre Some Statistical Issues in Microarray Data
  Analysis, pages 337--347.  \newblock Springer, 2003.

\item %{BDM02}
  J.-N. Bacro, J.-J. Daudin, S.~Mercier, and S.~Robin.  \newblock Back
  to the local score in the logarithmic case: a direct and simple
  proof.  \newblock {\em Ann. Inst. Statist. Math.}, 54:748--757,
  2002.

\item %{Rob02}
  S~Robin.  \newblock A compound {P}oisson model for words occurrences
  in {DNA} sequences.  \newblock {\em J. R. Statist. Soc. C},
  51:437--451, 2002.

\item %{RDR02}
  S.~Robin, J.-J. Daudin, H.~Richard, M.-F. Sagot, and S.~Schbath.
  \newblock Occurrence probability of structured motifs in random
  sequences.  \newblock {\em J. Comp. Biol.}, 9:761--773, 2002.

\item %{NRB01}
  G.~Nuel, S.~Robin, and C.~Baril.  \newblock Predicting phenotypic
  distances using a linear model: the case of varietal distinctness.
  \newblock {\em J. Appl. Statist.}, 28(5):607--621, 2001.

\item %{NBR01}
  G.~Nuel, C.~Baril, and S.~Robin.  \newblock Varietal distinctness
  assisted by molecular markers: A methodological approach.  \newblock
  {\em Acta Horticulturae}, 546:65--71, 2001.

\item %{SRD01}
  A.~Sekowska, S.~Robin, J.-J. Daudin, A.~H\'enaut, and A.~Danchin.
  \newblock Extracting biological information from dna arrays: an
  unexpected link between arginine and methionine metabolism in {\sl
    {b}acillus subtilis}.
  \newblock {\em Genome Biology}, 2(6): \\
  {\tt genomebiology.com/2001/2/6/research/0019.1}, 2001.

\item %{RoS01}
S.~Robin and S.~Schbath.
\newblock Numerical comparison of several approximations of the word count
  distribution in random sequences.
\newblock {\em J. Comp. Biol.}, 8(4):349--359, 2001.

\item %{RoD01}
S.~Robin and J.-J. Daudin.
\newblock Exact distribution of the distances between any occurrences of a set
  of words.
\newblock {\em Ann. Inst. Statist. Math.}, 36(4):895--905, 2001.

% \item %{Rob99}
% S.~Robin.
% \newblock A model for thermograms.
% \newblock {\em Biometrics}, 55(1):37--43, 1999.

% \item %{RoD99}
% S.~Robin and J.-J. Daudin.
% \newblock Exact distribution of word occurrences in a random sequence of
%   letters.
% \newblock {\em J. Appl. Prob.}, 36:179--193, 1999.

% \item %{DJR99}
% S.~Demotes-Mainard, M.-H. Jeuffroy, and S.~Robin.
% \newblock Spike dry matter and nitrogen accumulation before anthesis in wheat
%   as affected by nitrogen fertilizer: relationship to kernels per spike.
% \newblock {\em Field Crop Research}, 64:249--259, 1999.

% \item %{STR97}
% A.~Sahli, Ph. Tr\'ecourt, and S.~Robin.
% \newblock One sided acceptance sampling by variables: the case of the {L}aplace
%   distribution.
% \newblock {\em Commun. Statist. - Theory Meth.}, 26(11):2817--2834, 1997.

% \item %{Rob96}
% S.~Robin.
% \newblock Sensitivity analysis of non-parametric tests for censored data.
% \newblock {\em Commun. Statist. - Theory Meth.}, 25(8):1693--1715, 1996.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraphSR{Dans des revues internationales ŗ comitť de lecture.}

\begin{enumerate}

\item %{BaR03}
  A.~Bar-Hen and S.~Robin.  \newblock An iterative procedure for
  differential analysis of gene expression.  \newblock {\em C.-R.
    Acad. Sciences}, pages 343--346, 2003.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraphSR{Rapports de recherche.}

{\sl Ces documents correspondent ŗ des articles soumis et sont
  accessibles via internet.}
\begin{enumerate}
\item %{PDS07}
S.~Schbath F.~Picard, J.-J.~Daudin and S.~Robin.
\newblock Assessing the exceptionality of network motifs.
\newblock Research Report~1, INRA-Statistics for System Biology group, 2007.
\\ \newblock {\tt genome.jouy.inra.fr/ssb/preprint/SSB-RR-1.netmotifs.pdf}.

\item %{RBD07b}
A.~Bar-Hen S.~Robin and J.-J. Daudin.
\newblock Mixture model for random graphs: a variational approach.
\newblock Research Report~4, INRA-Statistics for System Biology group, 2007.
\\ \newblock {\tt genome.jouy.inra.fr/ssb/preprint/SSB-RR-4.ermg.pdf}.

\item %{PDR07}
S.~Robin F.~Picard, J.-J.~Daudin.
\newblock Mixture model for random graphs: a variational approach.
\newblock Research Report~3, INRA-Statistics for System Biology group, 2007.
\\ \newblock {\tt genome.jouy.inra.fr/ssb/preprint/SSB-RR-3.mixtureFDR.pdf}.

\item %{PLB07}
E.~Budinska F.~Picard, E.~Lebarbier and S.~Robin.
\newblock Joint segmentation of multivariate gaussian processes using mixed
  linear models.
\newblock Research Report~5, INRA-Statistics for System Biology group, 2007.
\\ \newblock {\tt genome.jouy.inra.fr/ssb/preprint/SSB-RR-5.mod\_mixed\_seg.pdf}.

\item %{DPR06}
J.-J. Daudin, F.~Picard, and S.~Robin.
\newblock A mixture model for random graphs.
\newblock Research Report 5840, INRIA, Feb. 2006.
\\ \newblock {\tt www.inria.fr/rrrt/rr-5840.html}.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraphSR{Confťrences invitťes (depuis 2001).} \label{Subsubsec:ConfInvit}
\begin{itemize}
% \item {\em Predicting phenotypic distances through molecular data}~:
%   Electrophoresis (Rouen, 1999).
\item {\em Analyse statistique des donnťes issues de biopuces},
  Journťes de la Sociťtť FranÁaise de Statistique (Bruxelles, 2002)
\item {\em Some Statistical Problems in Microarray Data Analysis}~:
  26th Annual Conference of the Gesellschaft fŁr Klassifikation
(Mannheim, Allemagne, 2002).
\item {\em Rťpartition de motifs dans des sťquences d'ADN}, Journťes
  de la Sociťtť FranÁaise de Statistique (Lyon, 2003)
\item {\em Analyzing Motifs Distribution in DNA Sequences}~: Theme
  Conference of the Royal Statistical Society on Statistical Genetics
  and Bioinformatics (Diepenbeck, Belgique, 2003).
\item {\em A segmentation/clustering approach for array CGH
    analysis}~: International Bioinformatics Workshop, Santiago,
  Chile, 2005
\item {\em Statistical analysis of CGH array data}, Heidelberg (All.),
  Septembre 2006
\item {\em Statistical Inference and Analysis of Biological Networks}
  Imperial College, Londres (GB), Octobre 2006.
\item {\em Statistical Bioinformatics and Stochastic Systems Biology
    Workshop}, universitť de Newcastle (GB), Avril 2007.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraphSR{Confťrences internationales (depuis 2004).}

Toutes les interventions indiquťes ici ont ťtť orales. Je n'indique
ici que les prťsentations que j'ai moi-mÍme effectuťes, pas celles dont
j'ťtait co-auteur.
\begin{itemize}
\item {\em Motif distribution in DNA sequences}, International
  Workshop on Applied Probability, AthŤnes (Gr), Avril
  2004. Confťrence avec actes.
\item {\em Checking heterogeneity of motif distribution in
    hťtťrogeneous sequences}, RECOMB conference, San Diego (USA), Mai
  2004. Confťrence avec actes.
\item {\em A mixture model for random graphs}~:
  \begin{itemize}
  \item EURANDOM, Eindhoven, Janvier 2006.
  \item International Workshop on Applied Probability, Unic.
    Connecticut (USA), Avril 2006. Confťrence avec actes.
  \end{itemize}
\end{itemize}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \paragraphSR{Sťminaires internationaux.} 
% \begin{itemize}
% \item {\em A statistical approach for array CGH data analysis},
%   Universidad Andrťs Bello, Santiago (Chili), Septembre 2005.
% \item {\em A semi-parametric approach for mixture models: Application
%     to local false discovery rate estimation}, Centre CNRS de
%   Modťlisation Mathťmatique, Santiago (Chili), , Septembre 2005
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SynthŤses scientifiques}

\paragraphSR{Dans des pťriodiques sans comitť de lecture.}
\begin{enumerate}
\item %[Robin (2003b)]{Rob03b}%
{\sc Robin, S.}
\newblock (2003).
\newblock La juste mesure des g\`{e}nes.
\newblock {\em La Recherche}.
\newblock {\bf (363)} 90--91.
\end{enumerate}


\paragraphSR{Chapitres d'ouvrages.}
\begin{enumerate}

\item %{BBD06}
A.~Bar-Hen, Ph. BroŽt, C.~Dalmasso, J.-J. Daudin, and S.~Robin.
\newblock {\em Encyclopedia of Biopharmaceutical Statistics}, chapitre False
  discovery rate.
\newblock Marcel Dekker: NewYork, 2nd edition, 2006.

\item %{MPR06}
T.~Mary-Huard, F.~Picard, and S.~Robin.
\newblock {\em Mathematical and Computational Methods in Biology}, chapitre
  Introduction to Statistical Methods for Microarray Data Analysis.
\newblock Hermann: Paris, 2006.

\item %{BDR06}
A.~Bar-Hen, J.-J. Daudin, and S.~Robin.
\newblock Comparaisons multiples pour les microarrays.
\newblock {\em J. Soc. FranÁaise Statis.}, 146(1-2):45--62, 2006.

\item %{MoB04}
P.~Doumas, C.~Rothan, and S.~Robin.
\newblock {\em La g\'enomique en biologie v\'eg\'etale}, chapitre Analyse du
  transcriptome v\'eg\'etal pas les puces ŗ ADN, pages 155--182.
\newblock Science update. INRA, 2004.

\item %{MMR04}
M.-L. Martin-Magnette and S.~Robin.
\newblock {\em Informatique pour l'analyse du transcriptome}, chapitre
  Techniques statistique pour l'analyse du transcriptome.
\newblock Herm\`es, 2004.

\end{enumerate}

\paragraphSR{Ouvrages.}
\begin{enumerate}
\item %[Robin {\em et al.} (2005)]{RRS05}%
{\sc Robin, S.}, {\sc Rodolphe, F.} et {\sc Schbath, S.}
\newblock (2005).
\newblock {\em {DNA}, words and models}.
\newblock Cambridge University Press, {\it ŗ paraÓtre}.
\item %[Robin {\em et al.} (2003a)]{RRS03}%
{\sc Robin, S.}, {\sc Rodolphe, F.} et {\sc Schbath, S.}
\newblock (2003).
\newblock {\em {ADN}, mots et modŤles}.
\newblock Echelles. Belin.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Documents ŗ vocation de transfert}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Travaux personnels}

\paragraphSR{Ouvrage.}
\begin{enumerate}
\item %[Daudin {\em et al.} (1999)]{DRV99}%
{\sc Daudin, J.-J.}, {\sc Robin, S.} et {\sc Vuillet, C.}
\newblock (1999).
\newblock {\em Statistique infťrentielle~: Idťes, dťmarches, exemples}.
\newblock Sociťtť FranÁaise de Statistique. Presses Universitaires de Rennes.
\end{enumerate}

\paragraphSR{Polycopiťs et supports de cours.}
\begin{enumerate}
\item %[Lebarbier et Robin (2004)]{LR-ExModLin}%
{\sc Lebarbier, E.} et {\sc Robin, S.}
\newblock (2004).
\newblock Exemples d'applications du modŤle linťaire.
\newblock 129p.

\item %[Robin (2003c)]{R-Biopuces}%
{\sc Robin, S.}
\newblock (2003).
\newblock Statistical analysis of microarray data.
\newblock 63p.

\item %[Duby et Robin (2001)]{DR-ACP}%
{\sc Duby, C.} et {\sc Robin, S.}
\newblock (2001).
\newblock Analyse en composantes principales.
\newblock 70p.

\item %[Doursat et Robin (1999)]{DR-SimRV}%
{\sc Doursat, C.} et {\sc Robin, S.}
\newblock (1999).
\newblock Simulating random values.
\newblock INA PG.

\item %[PommiŤs et Robin (1999)]{PR-CM}%
{\sc PommiŤs, E.} et {\sc Robin, S.}
\newblock (1999).
\newblock Introduction aux chaÓnes de markov homogŤnes.
\newblock 65p.

\item %[Robin (1999a)]{R-CSAGAD}%
{\sc Robin, S.}
\newblock (1999).
\newblock Cours de statistique du {CSAGAD}.
\newblock 200p.

\item %[Robin (1999b)]{R-Attente}%
{\sc Robin, S.}
\newblock (1999).
\newblock Introduction aux files d'attente.
\newblock 35p.

\item %[Robin (1999d)]{R-Poisson}%
{\sc Robin, S.}
\newblock (1999).
\newblock Processus de poisson, introduction aux processus de naissances et
  morts.
\newblock 22p.

\item %[Robin (1998)]{R-ModLin}%
{\sc Robin, S.}
\newblock (1998).
\newblock Rappels et complťments sur le modŤle linťaire.
\newblock 17p.

\item %[Daudin {\em et al.} (1996)]{DDRT-Chrono}%
{\sc Daudin, J.-J.}, {\sc Duby, C.}, {\sc Robin, S.} et {\sc Trťcourt, P.}
\newblock (1996).
\newblock Analyse des sťries chronologiques.
\newblock 70p.

\item %[Robin (1996a)]{R-CompPop}%
{\sc Robin, S.}
\newblock (1996).
\newblock Comparaison de populations.
\newblock 68p.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Travaux encadrťs}

\paragraphSR{Mťmoires de stage de DEA, DAA, DESS et Master.} \label{Subsec:Stages}
\begin{description}
\item[{\sl ModŤle de mťlange pour rťseaux d'interaction~:}]
  M. Mariadassou (2006)
\item[{\sl Tests multiples et validation croisťe~:}] A. Celisse (2005)
\item[{\sl Analyse de biopuces~:}] Ph. Hupť, F. Picard et T. Mary-Huard
  (2002), E. Haon-Lasporte (2004), O. Bagland (2005)
\item[{\sl Classification et FT-IR~:}] M. Lecomte (2001)
\item[{\sl Occurrences de motifs~:}] C. Jubin (1999), H. Richard (2000) et S.
  Ledent (2001)
\item[{\sl Distinction variťtale~:}] G. Nuel (1998), N. Legall (1999)
\item[{\sl Analyse de thermogrammes~:}] G. Bourguignon (1992), E. Gautherat
  (1995), D. Belhaj (1995)
\end{description}

% \newpage
% \input{Publis.bbl}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Dossier-DR2"
%%% End: 
