\noindent{Invitations aux frais de l'organisateur~:}
\begin{itemize}

\item
\newblock Uncovering structure in interaction networks.
\newblock In {\em Complex Networks Modeling Workshop}, SAMSI, Raleigh, USA,
  2010.

\item
\newblock Some statistical tools for change-points detection.
\newblock In {\em Homogenization in Climatological Databases {COST} action},
  Budapest, Hungary, 2011.

\item
\newblock Some statistical models and algorithms for change-point problems in
  genomics.
\newblock In {\em Statistical and dynamical models in biology and medicine},
  Stuttgart, Germany, 2012.

\item
\newblock Connexions between exponential random graph models and the stochastic
  block model.
\newblock In {\em Exponential random network models}, American Institute of
  Mathematics, Palo Alto, USA, 2013.

\item
\newblock Deciphering and modeling heterogeneity in interaction networks.
\newblock In {\em Classification and data analysis group}, Modena, Italy, 2013.

\item
\newblock Deciphering and modeling heterogeneity in interaction networks (using
  variational approximations).
\newblock In {\em Stats in {P}aris}, ENSAE, Malakoff, France, 2013.

\item
\newblock Exact ({B}ayesian) inference for change point models: {A}pplication
  to genomics.
\newblock In {\em Inference for Change Point and Related Processes}, Cambridge,
  {UK}, 2014.

\item
\newblock Network analysis with the {$W$}-graph model (via the stochastic block
  model).
\newblock In {\em Institute of Mathematics, Singapore: Program on Biological
  Networks}, Singapore, 2015.

\end{itemize}

\noindent{Invitations aux frais de mon laboratoire~:}
\begin{itemize}

\item
\newblock Averaging mixture models: a variational approximation.
\newblock In {\em Working group on model-based clustering}, Guelph, Canada,
  2012.

\item
\newblock Identifiability in hidden markov models applications to genomics.
\newblock In {\em Working group on model-based clustering}, Bologna, Italy,
  2013.

\item
\newblock Bayesian model averaging of stochastic block models to estimate the
  graphon function.
\newblock In {\em Computational and methodological statistics (ERCIM'14)},
  Pisa, Italy, 2014.

\item
\newblock Bayesian model averaging of stochastic block models to estimate the
  graphon function and motif frequencies in a w-graph model.
\newblock In {\em Working group on model-based clustering}, Dublin, Ireland,
  2014.

\item
\newblock Network analysis with the {$W$}-graph model (via the stochastic block
  model).
\newblock In {\em European Meeting of Statisticians}, Amsterdam, Netherlands,
  2015.

\item
\newblock Recurrent genomic alterations and excursions of markovian processes.
\newblock In {\em Stochastic Processes and their Applications}, Oxford, UK,
  2015.

\item
\newblock Unsupervised classification of species: Looking for adaptation shifts
  in evolution.
\newblock In {\em Working group on model-based clustering}, Seattle, USA, 2015.

\end{itemize}
